refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-08-13 paper/manuscript.tex
Fix bibliography for iucr
- Use a vendored version of iucr.bst if available
  iucr.bst doesn't actually match the instructions to authors
- Fix various parts of .bib file so that it is rendered correctly
- Fix data in .bib file
Add extra refs

@@

In order for a given scattering analysis to be fully reproducible by others, a general set of conditions need to be met:
\begin{itemize}
  \item the processed datasets used in the analysis need to be deposited with a journal article, or be freely available. Ideally the raw datasets, and the means to create the processed datasets should also be made available.
  \item the exact software environment needs to be recreatable.
  \item the exact ordered set of steps taken during the analysis needs to be listed.
\end{itemize} 
Each of these points are often omitted in the literature. For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may preclude recording the full set of steps, or options, applied by a user. Whilst it is unable to meet the first criterion by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken. As we have already noted, the ordered set of steps to perform the analysis is the \Jupyter\ notebook in which the analysis was performed and this is an artefact able to be archived.

@@

The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here. With closed source or proprietary software, the ability to return to a specific software version/environment can be frustrated, and different versions can have modifications that can unknowingly change the output of an analysis. In addition reduced accessibility (due to cost, etc) to the wider scientific community can also hinder reproducibility.

Moreover, there are important ramifications for verifiability. \refnx\ is based on a fully open software stack, with good unit test coverage. The user can run tests for each component and inspect parts for correctness. For example, the behaviour of the reflectivity calculation in \refnx\ is checked from first principles in the test suite; and can be done now and in several years time. If problems are discovered, they can be corrected. With a closed source program such checking is harder, one has to examine the inputs/outputs of a black box without knowing what is happening in between, making it harder to find errors; one has to rely on trust. Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.
%include citation
%FIXME: this is a hypothesis, without being able to see the testing practices and codebases of proprietary programs it's hard to tell. However, given that open source software has bugs, it's safe to say that these will also occur in proprietary programs.

@@

\bibliography{main}{}
\bibliographystyle{iucr}
\end{document}

>>>>

% \usepackage[colorlinks,urlcolor=black]{hyperref}
\renewcommand{\harvardurl}[1]{\url{#1}}
\newcommand{\url}[1]{#1}

@@

In order for a given scattering analysis to be fully reproducible by others, a general set of conditions need to be met \cite{Helliwell2017, Moeller2017a}:
\begin{itemize}
  \item the processed datasets used in the analysis need to be deposited with a journal article, or be freely available. Ideally the raw datasets, and the means to create the processed datasets should also be made available.
  \item the exact software environment needs to be recreatable.
  \item the exact ordered set of steps taken during the analysis needs to be listed.
\end{itemize} 
Each of these points is often inadequately addressed in the literature. For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may preclude recording the full set of steps, or options, applied by a user \cite{Chirigati2013}. Whilst it is unable to meet the first criterion by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken. As we have already noted, the ordered set of steps to perform the analysis is the \Jupyter\ notebook in which the analysis was performed and this is an artefact able to be archived.

@@

The usefulness of open-source software in a git (or other version controlled) repository must be emphasised here \cite{Moeller2017a}. With closed source or proprietary software, the ability to return to a specific software version/environment can be frustrated, and different versions can have modifications that can unknowingly change the output of an analysis. In addition reduced accessibility (due to cost, etc) to the wider scientific community can also hinder reproducibility.

Moreover, there are important ramifications for verifiability \cite{Chirigati2013}. \refnx\ is based on a fully open software stack, with good unit test coverage. The user can run tests for each component and inspect parts for correctness. For example, the behaviour of the reflectivity calculation in \refnx\ is checked from first principles in the test suite; and can be done now and in several years time. If problems are discovered, they can be corrected. With a closed source program such checking is harder, one has to examine the inputs/outputs of a black box without knowing what is happening in between, making it harder to find errors; one has to rely on trust. Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.

@@

\bibliography{main}{}

% the provided iucr.bst doesn't match the journal style but a fixed version
% is not redistributable.
\IfFileExists{iucrdoi.bst}{
  \bibliographystyle{iucrdoi}
}{
  \bibliographystyle{iucr}
}
\end{document}
